---
title: "Functions of the farsAJS package"
author: "ajsarradin"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
  fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Functions of the farsAJS package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r packages, include=F}

# I should underline that vignette is build automatically when your build your package. So, when development are finish, replace in the vignette devtools::load_all by library because your package is loaded before building the vignette when you build a package.

#devtools::load_all(getwd())
library(farsAJS)

```

The **farsAJS** package offers several functions that make it easier to read, filter, summarise, and plot data for road accidents from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS).

<br/>

**filename** returns the file name from the FARS data that contains the *year* specified by the user. To be used in combination with **fars_read**.

```{r make_filename}
year<-c(2013)
filename<-make_filename(year)
filename

```

**fars_read** reads a csv file and converts it into a *tbl_df* table. It can be used in combination with **filename**.

```{r fars_read}
ds<-fars_read(filename)
head(ds)

```

**fars_read_years** reads one or more csv files, converts them into *tbl_df* tables, extracts *year* and *month*
information from these tables and stores the result in a *list* object with one entry per year.

```{r fars_read_years}
fars_read_years(2013)
fars_read_years(2013:2015)[[2]]

```

**fars_summarize_years** reads one or more csv files, converts them into *tbl_df* tables, extracts *year* and *month*
information from these tables, counts the number of observations per month for each year and stores the result
in a *tbl_df* table with one column per year.

```{r fars_summarize_years}
fars_summarize_years(2013:2015)

```

**fars_map_state** plots location data for a US state and year specified by the user.

```{r fars_map_state, fig.show='hold', fig.cap ="Your figure caption"}
fars_map_state(28,2014)
fars_map_state(54,2015)

```


